### 2021-05-03 Paper/Results.tex
latex now basically to the end!!
Updates from Overleaf

\begin{center}
    \paperspacingnarrow
    \input{Code/data/FF_pass_2}\\
    \textbf{Table 3:} second pass results for the size and beta decile portfolios\\
    \paperspacingwide
\end{center}

@@

\begin{center}
    \paperspacingnarrow
    \input{Code/data/All_Industry_FF_pass_2}\\
    \textbf{Table 5:} SIC top 10\% minus bottom 10\%
    \paperspacingwide
\end{center}

>>>>

\begin{center}
    \paperspacingnarrow
    \input{Code/data/FF_pass_2}\\
    \textbf{Table 3:} shows the results for the Second pass of the twp pass sort. On the left labeled as (1) are the regression results for the size decile portfolios. On the right labeled as (2) are the regression results for the beta decile portfolios\\
    \paperspacingwide
\end{center}

@@

\begin{center}
    \paperspacingnarrow
    \input{Code/data/All_Industry_FF_pass_2}\\
    \textbf{Table 5:} SIC top 10\% minus bottom 10\% \hl{NEED TO EDIT THESE RESULTS}
    \paperspacingwide
\end{center}
